Exploratory data analysis

### 2019-06-21 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE)

```{r eda-17, dev = c("png", "pdf")}
boxplot_defol <- vi_data_plot %>%
  group_by(plot) %>%
  ggboxplot(
    x = "plot", y = "defoliation", color = "plot",
    add = "jitter", add.params = list(size = "defoliation")
  ) +
  scale_size(range = c(0.5, 0.5)) +
  annotate("text",
    label = expression(bold(atop("n = 479", bar(x) ~ "= 55.96"))), x = 1,
    y = 112, size = 3, colour = "#BC3C29", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 451", bar(x) ~ "= 13.54"))), x = 2,
    y = 112, size = 3, colour = "#0072B5", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 300", bar(x) ~ "= 68.44"))), x = 3,
    y = 112, size = 3, colour = "#E18727", fontface = 2
  ) +
  annotate("text",
    label = expression(bold(atop("n = 529", bar(x) ~ "= 69.22"))), x = 4,
    y = 112, size = 3, colour = "#20854E", fontface = 2
  ) +
  scale_color_nejm() +
  theme(legend.position = "none") +
  labs(y = "Total defoliation per tree (%)", x = "Plot")
boxplot_defol
```

@@

```{r eda-19, echo = FALSE}
file_move("docs/figure/eda.Rmd/defoliation-distribution-plot-1.pdf",
          "code/98-paper/journal/")
```

@@

fv_all = dplyr::bind_rows(fv_vi_car$data, 
                          fv_vi_info.gain$data, 
                          fv_vi_gain.ratio$data,
                          fv_vi_rank$data, 
                          fv_vi_cor$data, 
                          fv_vi_mrmr, 
                          fv_vi_cmim$data, 
                          fv_vi_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 7)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

fv_all = dplyr::bind_rows(fv_nri_car$data, 
                          fv_nri_info.gain$data, 
                          fv_nri_gain.ratio$data,
                          fv_nri_rank$data, 
                          fv_nri_cor$data, 
                          fv_nri_mrmr, 
                          fv_nri_cmim$data, 
                          fv_nri_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 7)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

fv_all = dplyr::bind_rows(fv_hr_car$data, 
                          fv_hr_info.gain$data, 
                          fv_hr_gain.ratio$data,
                          fv_hr_rank$data, 
                          fv_hr_cor$data, 
                          fv_hr_mrmr, 
                          fv_hr_cmim$data, 
                          fv_hr_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 7)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

>>>>

```{r defoliation-distribution-plot, dev = c("png", "pdf")}
boxplot_defol <- vi_data_plot %>%
  group_by(plot) %>%
  ggboxplot(
    x = "plot", y = "defoliation", color = "plot",
    add = "jitter", add.params = list(size = "defoliation")
  ) +
  scale_size(range = c(0.5, 0.5)) +
  annotate("text",
           label = expression(bold(atop("n = 479", bar(x) ~ "= 55.96"))), x = 1,
           y = 112, size = 3, colour = "#BC3C29", fontface = 2
  ) +
  annotate("text",
           label = expression(bold(atop("n = 451", bar(x) ~ "= 13.54"))), x = 2,
           y = 112, size = 3, colour = "#0072B5", fontface = 2
  ) +
  annotate("text",
           label = expression(bold(atop("n = 300", bar(x) ~ "= 68.44"))), x = 3,
           y = 112, size = 3, colour = "#E18727", fontface = 2
  ) +
  annotate("text",
           label = expression(bold(atop("n = 529", bar(x) ~ "= 69.22"))), x = 4,
           y = 112, size = 3, colour = "#20854E", fontface = 2
  ) +
  scale_color_nejm() +
  theme(legend.position = "none") +
  labs(y = "Total defoliation per tree (%)", x = "Plot")
boxplot_defol
```

@@

```{r eda-19, echo = FALSE}
# file_move("docs/figure/eda.Rmd/defoliation-distribution-plot-1.pdf",
#           "code/98-paper/journal/")
```

@@

fv_all = dplyr::bind_rows(fv_vi_car$data, 
                          fv_vi_info.gain$data, 
                          fv_vi_gain.ratio$data,
                          fv_vi_rank$data, 
                          fv_vi_cor$data, 
                          fv_vi_mrmr$data, 
                          fv_vi_cmim$data, 
                          fv_vi_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:89, 8)) %>% 
  tidyr::spread(method, value) %>% 
  mutate_if(is.numeric, list(~na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

corr = cor(fv_all)
#p.mat = cor_pmat(corr)

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = F,
           type = "lower",
           lab = TRUE)
```

@@

fv_all = dplyr::bind_rows(fv_nri_car$data, 
                          fv_nri_info.gain$data, 
                          fv_nri_gain.ratio$data,
                          fv_nri_rank$data, 
                          fv_nri_cor$data, 
                          fv_nri_mrmr$data, 
                          fv_nri_cmim$data, 
                          fv_nri_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 8)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

fv_all = dplyr::bind_rows(fv_hr_car$data, 
                          fv_hr_info.gain$data, 
                          fv_hr_gain.ratio$data,
                          fv_hr_rank$data, 
                          fv_hr_cor$data, 
                          fv_hr_mrmr$data, 
                          fv_hr_cmim$data, 
                          fv_hr_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:122, 8)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = F,
           type = "lower",
           lab = TRUE)
```
